Search for WIMP Inelastic Scattering Off Xenon Nuclei With XENON100

### 2017-06-13 Inelastic/results.tex
version uploaded to archive
response to referee, first draft

\begin{figure}[t]
  \includegraphics[width=\linewidth]{images/data_vs_bkg.png}
  \caption{Distribution of  observed events  in the region of interest (data points), along with the normalized distribution from calibration data (filled histogram). The bottom panel displays the ratio
between data and expected background, where the light  and dark blue shaded areas represent the statistical and systematic uncertainty 
on the background expectation, respectively. The expected signal for a WIMP mass of 100\,GeV/c$^2$ (blue dashed), normalized to a total of 50 events, is also shown.}
  \label{fig:dataVSbkg}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=\linewidth]{images/limit_reb.png}
  \caption{Upper limit (blue curve) on the spin-dependent, inelastic WIMP-nucleon cross section as a function of WIMP mass.  
	  %The expected median sensitivity (dashed curve) along with 
	  The expected one (light shaded area) and two (dark shaded area) standard deviation uncertainty is also shown. 
	  This result is compared to the upper limit (at 90\% C.L.) obtained by the XMASS experiment (dashed line)~\cite{Uchida:2014cnn}.}
  \label{fig:limits}
\end{figure}

This result is interpreted via a binned profiled likelihood approach by means of the test statistic $\tilde{q}$
and its asymptotic distributions, as  described in \cite{asympt}. 
Assuming  an isothermal WIMP halo with a local density of $\rho_{\chi} \, = \, 0.3$\,GeV/cm$^3$, a local circular velocity of $v_0 \,= \, 220$\,km/s, 
a galactic escape velocity of $v_{\rm{esc}} \, = \, 544$\,km/s~\cite{Smith:2006ym}  
and the nuclear structure factors as computed in~\cite{Baudis:2013bba}, 
a 90\% CL$_s$~\cite{cls} confidence level upper limit is set on the spin-dependent inelastic WIMP-nucleon cross section as a function of the WIMP mass. 
%\sout{We employ the nuclear structure factors as calculated in \cite{Baudis:2013qla}, based on state-of-the-art large-scale shell-model calculations, with chiral effective field theory WIMP-nucleon currents.}

>>>>

\begin{figure}[t]
  \includegraphics[width=\linewidth]{data_vs_bkg.png}
  \caption{Distribution of  observed events  in the region of interest (data points), along with the normalized distribution from calibration data (filled histogram). The expected signal for a WIMP mass of 100\,GeV/c$^2$ (blue dashed), normalized to a total of 50 events, is also shown. 
	  The bottom panel displays the ratio between data and expected background, where the light  and dark blue shaded areas represent the statistical and systematic uncertainty on the background expectation, respectively. }
  \label{fig:dataVSbkg}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=\linewidth]{limit_reb.png}
  \caption{Upper limit (blue curve) on the spin-dependent, inelastic WIMP-nucleon cross section as a function of WIMP mass.  
	  %The expected median sensitivity (dashed curve) along with 
	  The expected one (light shaded area) and two (dark shaded area) standard deviation uncertainty is also shown. 
	  This result is compared to the upper limit (at 90\% C.L.) obtained by the XMASS experiment (dashed line)~\cite{Uchida:2014cnn}.}
  \label{fig:limits}
\end{figure}

This result is interpreted via a binned profiled likelihood approach by means of the test statistic $\tilde{q}$
and its asymptotic distributions, as  described in \cite{asympt}. 
Assuming  an isothermal WIMP halo with a local density of $\rho_{\chi} \, = \, 0.3$\,GeV/cm$^3$, a local circular velocity of $v_0 \,= \, 220$\,km/s, 
a galactic escape velocity of $v_{\rm{esc}} \, = \, 544$\,km/s~\cite{Smith:2006ym}  
and the nuclear structure factors as computed in~\cite{Baudis:2013bba}, 
a 90\% CL$_s$~\cite{cls} confidence level upper limit is set on the spin-dependent inelastic WIMP-nucleon cross section as a function of the WIMP mass. 
%\sout{We employ the nuclear structure factors as calculated in \cite{Baudis:2013qla}, based on state-of-the-art large-scale shell-model calculations, with chiral effective field theory WIMP-nucleon currents.}
{\ale The CL$_s$ technique helps protecting against exclusion of a cross section
smaller than experimental sensitivity.}
